---
title: 'Exploratory Factor Analysis - Populism Outcomes'
output: pdf_document
---

```{r setup, message=FALSE, warning=FALSE}
# Load packages
pacman::p_load(tidyverse, here, psych, GPArotation, corrplot)

# Define levels for populism items
pop_levels <- c('Strongly Disagree', 'Somewhat Disagree', 'Neither', 'Somewhat Agree', 'Strongly Agree')

# Load Pilot 2 and Pilot 3 data
df_p2 <- read_csv(here('experiment/data/populism and news3.csv')) %>% mutate(pilot = 'pilot2') %>% filter(!is.na(Q_second_order_1))
df_p3 <- read_csv(here('experiment/data/pilot3.csv')) %>% mutate(pilot = 'pilot3')

# Combine and create populism variables
df <- bind_rows(df_p2, df_p3) %>%
  mutate(
    # Attention check (pilot2 only)
    att = case_when(
      Q_att1 != 'Somewhat disagree' ~ 'Failed attention check',
      `Duration (in seconds)` < 240 ~ 'Speeder',
      TRUE ~ 'N/A'
    ),

    # Populism items
    will_of_ppl = ordered(Q_pop1, levels=pop_levels) %>% as.numeric(),
    power_improve_rev = ordered(Q_pop2, levels=rev(pop_levels)) %>% as.numeric(),
    system_stacked = ordered(Q_pop3, levels=pop_levels) %>% as.numeric(),
    trust_experts_rev = ordered(Q_pop4, levels=rev(pop_levels)) %>% as.numeric(),
    good_corrupt = ordered(Q_pop5, levels=pop_levels) %>% as.numeric(),
    leader_represent = ordered(Q_pop6, levels=pop_levels) %>% as.numeric(),
    ordinary_represent_rev = ordered(Q_pop7, levels=rev(pop_levels)) %>% as.numeric(),
    ordinary_policies_rev = ordered(Q_pop8, levels=rev(pop_levels)) %>% as.numeric(),
    rely_experts_too_much = ordered(Q_pop9, levels=pop_levels) %>% as.numeric(),
    rely_experts_rev = ordered(Q_pop9_rev, levels=rev(pop_levels)) %>% as.numeric(),
    experts_claim = ordered(Q_pop10, levels=pop_levels) %>% as.numeric(),
    unfair_system = ordered(Q_pop11, levels=pop_levels) %>% as.numeric(),

    # Additional items
    news_trust_rev = ordered(Q_news_trust, levels=rev(c('Not at all', 'Not too much', 'Some', 'A fair amount', 'A lot'))) %>% as.numeric(),
    conpress_rev = case_when(
      Q_conpress == 'Hardly any' ~ 5,
      Q_conpress == 'Only some' ~ 3,
      Q_conpress == 'A great deal' ~ 1,
      TRUE ~ NA_real_
    )
  )
```

# Overview

This document performs exploratory factor analysis (EFA) on the six outcome variables:
- will_of_ppl: The will of the people should be the highest principle in this country's politics
- power_improve_rev: Politicians and elites use their power to try to improve people's lives (reverse coded)
- system_stacked: The system is stacked against people like me
- trust_experts_rev: I'd rather put my trust in the opinions of experts than the wisdom of ordinary people (reverse coded)
- good_corrupt: Politics is a fight between the good people and the corrupt elite
- news_trust_post: Trust in media/news

# Descriptive Statistics

```{r}
# Select outcome variables for EFA

outcomes <-
df %>% select(
    will_of_ppl,
    good_corrupt,
    leader_represent,
    ordinary_represent_rev,
    ordinary_policies_rev,
    system_stacked,
    unfair_system,
    power_improve_rev,
    trust_experts_rev,
    experts_claim,
    rely_experts_too_much,
  ) %>% na.omit()
outcomes <-
df %>% select(
    will_of_ppl,
    good_corrupt,
    leader_represent,
    ordinary_represent_rev,
    ordinary_policies_rev,
    system_stacked,
    unfair_system,
    power_improve_rev,
    trust_experts_rev,
    experts_claim,
    rely_experts_too_much,
  ) %>% na.omit()
# Summary statistics
summary(outcomes)
nrow(outcomes)

# Check sample size
cat("Sample size:", nrow(outcomes), "\n")
```

# Correlation Matrix

```{r}
# Correlation matrix
cor_matrix <- cor(outcomes)
print(round(cor_matrix, 2))

# Visualize correlations
library(corrplot)
corrplot(cor_matrix, method = "number", type = "upper",
         tl.col = "black", tl.srt = 45,
         title = "Correlation Matrix of Outcome Variables",
         mar = c(0,0,2,0))
```


# Bartlett's Test and KMO

Testing whether the data is suitable for factor analysis.

```{r}
# Bartlett's test of sphericity (tests if correlation matrix is identity matrix)
# cortest.bartlett(cor_matrix, n = nrow(outcomes))

# Kaiser-Meyer-Olkin (KMO) measure of sampling adequacy
# Values > 0.6 are acceptable, > 0.8 is good
KMO(outcomes)
```

# Determining Number of Factors

```{r}
# Scree plot
scree(outcomes, factors = FALSE, main = "Scree Plot")

# Parallel analysis - compares eigenvalues to random data
fa.parallel(outcomes, fa = "fa", n.iter = 100,
            main = "Parallel Analysis Scree Plots")

# Very Simple Structure (VSS) criterion
vss(outcomes, rotate = "varimax", plot = TRUE)

# Eigenvalues
eigenvalues <- eigen(cor_matrix)$values
cat("\nEigenvalues:\n")
print(round(eigenvalues, 2))
cat("\nProportion of variance explained:\n")
print(round(eigenvalues / sum(eigenvalues), 2))
```

# Factor Analysis with Different Numbers of Factors

## 1-Factor Solution

```{r}
fa1 <- fa(outcomes, nfactors = 1, rotate = "none", fm = "ml")
print(fa1, cut = 0.3, digits = 3)
```

## 2-Factor Solution

```{r}
# Try different rotation methods
fa2_varimax <- fa(outcomes, nfactors = 2, rotate = "varimax", fm = "ml")
fa2_oblimin <- fa(outcomes, nfactors = 2, rotate = "oblimin", fm = "ml")

print(fa2_varimax, cut = 0.3, digits = 3)
print(fa2_oblimin, cut = 0.3, digits = 3)

# Visualize factor loadings
fa.diagram(fa2_varimax, main = "2-Factor Solution (Varimax)")
fa.diagram(fa2_oblimin, main = "2-Factor Solution (Oblimin)")
```

Ok clearly ordinary_policies_rev doesnt load onto anything. 
Lets remove it and rerun the factor analysis
### Model Refinement

**Key issues to address:**
1. `ordinary_policies_rev` doesn't load on either factor
2. Redundancy between `system_stacked` and `unfair_system`
3. `power_improve_rev` conceptually doesn't fit people-centric dimension
4. Weak loadings: `ordinary_represent_rev` and `good_corrupt`

```{r}
# Systematic model comparison
model_a <- fa(outcomes %>% select(-ordinary_policies_rev),
              nfactors=2, rotate='varimax', fm='ml')

model_b <- fa(outcomes %>% select(-ordinary_policies_rev, -unfair_system),
              nfactors=2, rotate='varimax', fm='ml')

model_c <- fa(outcomes %>% select(-ordinary_policies_rev, -power_improve_rev, -unfair_system),
              nfactors=2, rotate='varimax', fm='ml')

model_d <- fa(outcomes %>% select(-ordinary_policies_rev, -power_improve_rev,
                                   -unfair_system, -ordinary_represent_rev),
              nfactors=2, rotate='varimax', fm='ml')

model_e <- fa(outcomes %>% select(-ordinary_policies_rev, -power_improve_rev,
                                   -unfair_system, -ordinary_represent_rev, -good_corrupt),
              nfactors=2, rotate='varimax', fm='ml')

model_f <- fa(outcomes %>% select(-ordinary_policies_rev, -power_improve_rev,
                                   -unfair_system, -ordinary_represent_rev, -trust_experts_rev),
              nfactors=2, rotate='varimax', fm='ml')

# Model comparison table
models <- list(
  "A: Drop policies (10 items)" = model_a,
  "B: + drop unfair_system (9)" = model_b,
  "C: + drop power_improve (8)" = model_c,
  "D: + drop ordinary_rep (7)" = model_d,
  "E: + drop good_corrupt (6)" = model_e,
  "F: + drop trust_experts (6)" = model_f
)

fit_table <- data.frame(
  Model = names(models),
  N_items = sapply(models, function(x) ncol(x$loadings)),
  Chi_sq = sapply(models, function(x) round(x$STATISTIC, 2)),
  p = sapply(models, function(x) round(x$PVAL, 3)),
  RMSEA = sapply(models, function(x) round(x$RMSEA[1], 3)),
  TLI = sapply(models, function(x) round(x$TLI, 3)),
  BIC = sapply(models, function(x) round(x$BIC, 1))
)

knitr::kable(fit_table, caption = "Model Fit Comparison")

```

# Internal Consistency

```{r}
# The best model was model d

outcomes_drop3 <- outcomes %>% select(-ordinary_policies_rev, -power_improve_rev, -unfair_system, -ordinary_represent_rev)
psych::alpha(outcomes_drop3)$total$raw_alpha
# People centric scale not terrible: alpha 0.65
psych::alpha(outcomes %>% select(will_of_ppl, good_corrupt, leader_represent, system_stacked))$total$raw_alpha

psych::alpha(outcomes %>% select(will_of_ppl, leader_represent, system_stacked))$total$raw_alpha

psych::alpha(outcomes %>% select(will_of_ppl, leader_represent, good_corrupt))$total$raw_alpha

# The anti elite scale is better: alpha 0.73
psych::alpha(outcomes %>% select(trust_experts_rev, experts_claim, rely_experts_too_much))$total$raw_alpha
# We could drop a question if we wanted to
psych::alpha(outcomes %>% select(experts_claim, rely_experts_too_much))$total$raw_alpha
psych::alpha(outcomes %>% select(experts_claim, trust_experts_rev))$total$raw_alpha
psych::alpha(outcomes %>% select(experts_claim, trust_experts_rev))$total$raw_alpha
psych::alpha(outcomes %>% select(rely_experts_too_much, trust_experts_rev))$total$raw_alpha
```

# Are media trust and anti elite sentiment correlated?

```{r}
outcomes_ae <- df %>% select(experts_claim, rely_experts_too_much, trust_experts_rev, conpress_rev, news_trust_rev)
cor(outcomes_ae, use='complete')
fa(outcomes_ae, nfactors = 1, rotate = "varimax", fm = "ml")
fa(outcomes_ae, nfactors = 2, rotate = "varimax", fm = "ml")
fa(outcomes_ae %>% select(-trust_experts_rev), nfactors = 2, rotate = "varimax", fm = "ml")
# Much better without trust_experts_rev haha
```

# Checking expert_rev

```{r}
outcomes <-
df %>% select(
    will_of_ppl,
    good_corrupt,
    leader_represent,
    ordinary_represent_rev,
    ordinary_policies_rev,
    system_stacked,
    unfair_system,
    power_improve_rev,
    trust_experts_rev,
    experts_claim,
    rely_experts_rev,
    rely_experts_too_much,
  ) %>% na.omit()
fa(outcomes %>% select(-ordinary_policies_rev, -power_improve_rev, -unfair_system, -ordinary_represent_rev), nfactors=2, rotate='varimax', fm='ml')
cor(df$rely_experts_too_much, df$rely_experts_rev, use='complete')
```


